### 2024-08-26 manuscript.tex
Various updates

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/lts_dist.pdf}
\caption{
Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
the highest instantaneous temporal resolution data. Shown is also the chosen
dividing threshold of 12 K for `stable' and `unstable' conditions.
}
\label{fig:lts-dist}
\end{figure}

@@

We partitioned our data into subsets by cyclonic activity. For this purpose,
we used a cyclone tracking algorithm to identify extratropical and polar
cyclones (ECs and PCs) over the SO in the reanalysis and ICON data,
We used the open source cylone tracking package CyTRACK
\citep{perez-alarcon2024}. Generally, what constitutes an EC is considered
relatively arbitrary due to a very large variability of ECs \citep{neu2013}.
We used the mean sea level pressure field and horizontal wind speed fields as
input to the CyTRACK algorithm. The algorithm uses pressure and wind speed
thresholds as well as tracking across time steps to identify cyclone centres
and radii. From this information, we could classify geographical areas as
either cyclonic or non-cyclonic. Due to a relatively small total area covered,
we chose a circle of a double radius (relative to one identified by CyTRACK)
centred at the cyclone centre as a cyclonic area for every time step and
cyclone. All other areas were identified as non-cyclonic.  For identifying
cyclones in the observations, ERA5 pressure and wind fields were used as the
input to CyTRACK. This is justified by the fact that large-scale pressure and
wind fields are likely sufficiently close to the reality in ERA5. For
identifying cyclones in ICON, ERA5, MERRA-2, their own pressure and wind fields
were used as the input to CyTRACK.

@@

We determine stability by calculating lower tropospheric stability (LTS)
as the difference between potential temperature at 700 hPa and the surface.
From a histogram of LTS in ERA5 and MERRA-2 calculated at all voyage tracks
and the station (Fig. S1), we determined a dividing threshold of 12 K for
relatively unstable (< 12 K) and relatively stable (>= 12 K) conditions.

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/lts_dist.pdf}
\caption{
Lower tropospheric stability (LTS) distribution in \textbf{(a)} ERA5 and
\textbf{(b)} MERRA-2 calculated for the 31 voyage tracks and one station from
the highest instantaneous temporal resolution data available. Shown is also the
chosen dividing threshold of 12 K for `stable' and `unstable' conditions.
}
\label{fig:lts}
\end{figure}

@@

We partitioned our data into two subsets by cyclonic activity. For this
purpose, we used a cyclone tracking algorithm to identify extratropical and
polar cyclones (ECs and PCs) over the SO in the reanalysis and ICON data, We
used the open source cylone tracking package CyTRACK \citep{perez-alarcon2024}.
Generally, what constitutes an EC is considered relatively arbitrary due to a
very large variability of ECs \citep{neu2013}.  We used the mean sea level
pressure field and horizontal wind speed fields as input to the CyTRACK
algorithm. The algorithm uses pressure and wind speed thresholds as well as
tracking across time steps to identify cyclone centres and radii. From this
information, we could classify geographical areas as either cyclonic or
non-cyclonic. Due to a relatively small total area covered, we chose a circle
of a double radius (relative to one identified by CyTRACK) centred at the
cyclone centre as a cyclonic area for every time step and cyclone. All other
areas were identified as non-cyclonic. For identifying cyclones in the
observations and the reanalyses, ERA5 pressure and wind fields were used as the
input to CyTRACK.  This is justified by the fact that the large-scale pressure
and wind fields in ERA5 are likely sufficiently close to the reality. For
identifying cyclones in ICON, its own pressure and wind fields were used as the
input to CyTRACK, because the model is free-running, and thus the pressure and
wind fields are different from reality.

@@

We partitioned our data into two subset by stability. We determined this by
calculating lower tropospheric stability (LTS) as the difference between
potential temperature at 700 hPa and the surface.  Based on a histogram of LTS
in ERA5 and MERRA-2 calculated at all voyage tracks and stations (Fig.
\ref{fig:lts}), we determined a dividing threshold of 12 K for relatively
unstable (< 12 K) and relatively stable (>= 12 K) conditions.
